\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\input{sym}
\title{Homework 3: Minimum cost circuits using K-maps}
\author{Max marks: 155}
\date{Due on September 29, 2023, 12:00 noon, in the beginning class. Please
submit an official copy on brightspace. Please submit a paper copy in class.
The paper copy is recommended, but not required. It is easier to grade on
paper. }
\newtheorem{prob}{Problem}

\newcommand{\bx}{\bar{x}}
\newcommand{\by}{\bar{y}}
\newcommand{\bz}{\bar{z}}
\newcommand{\bA}{\bar{A}}
\newcommand{\bB}{\bar{B}}
\newcommand{\bC}{\bar{C}}
\begin{document}

\maketitle

\begin{prob}
  Read Chapter 2 up to Section 2.7 of Harris and Harris textbook. Write a statement saying that you have read and understood the chapter. [5 marks]
\end{prob}

\begin{prob}
If the Sum of Products (SOP) form for $ \bar{f} = AB\bC+\bA\bB$, then give the Product of Sums (POS) form for
$f$. [10 marks]
\end{prob}

\begin{prob}
Use DeMorgan's Theorem to find $f$  if  $\bar{f} = (A + \bB C)D + EF$. [10 marks]
\end{prob}


\begin{prob}
  For the function $f = AB\bC + BD$,
  \begin{enumerate}
    \item Write the Truth table. [10 marks]
    \item Write $f$ in Sum of Products form. [10 marks]
    \item Write $f$ in canonical minterm form. [10 marks]
    \item Write $f$ as Product of Sums. [10 marks]
    \item Write $f$ in canonical maxterm form. [10 marks]
  \end{enumerate}
\end{prob}

\begin{table}
  \centering
  \begin{tabular}{c|ccc||c}
    \toprule
    Row & $x_1$ & $x_2$ & $x_3$ & f \\
    \midrule
    0 & 0 & 0 & 0 & 0 \\
    1 & 0 & 0 & 1 & 1 \\
    2 & 0 & 1 & 0 & 1 \\
    3 & 0 & 1 & 1 & 0 \\
    4 & 1 & 0 & 0 & 1 \\
    5 & 1 & 0 & 1 & 0 \\
    6 & 1 & 1 & 0 & 0 \\
    7 & 1 & 1 & 1 & 1 \\
    \bottomrule
    \end{tabular}
    \caption{Truth table for a 3-way light switch}
    \label{tab:3-way-light-switch}
\end{table}

\begin{prob}
 Implement the function in Table~\ref{tab:3-way-light-switch} using only NAND
 gates. [10 marks]
\end{prob}

\begin{prob}
 Implement the function in Table~\ref{tab:3-way-light-switch} using only NOR
 gates. [10 marks]
\end{prob}

%\section{Sept 13th Lecture}

\begin{prob}
Find the minimum-cost Sum of Products (SOP) and Product of Sums (POS) forms for the function $f(x_1 , x_2 , x_3 ) =
m(1, 3, 4, 5)$.  Chose the minimum-cost expression by comparing Product of Sums (POS) and Sum of Products (SOP) forms. [10 marks]
\label{prob:237}
\end{prob}

\begin{prob}
Find the minimum-cost Sum of Products (SOP) and Product of Sums (POS) forms for the function $f(x_1 , x_2 , x_3) =
\sum m(1, 5, 7) + D(2, 4)$.  [10 marks]
\end{prob}

\begin{prob}
Find the minimum-cost Sum of Products (SOP) and Product of Sums (POS) forms for the function $f(x_1 , x_2 , x_3,
x_4) = \prod M(1, 2, 4, 5, 7, 8, 9, 10, 12, 14, 15).$  Chose the minimum-cost
expression by comparing Product of Sums (POS) and Sum of Products (SOP) forms. [10 marks]
\end{prob}

\begin{prob}
Find the minimum-cost Sum of Products (SOP) and Product of Sums (POS) forms for the function $f(x_1 , x_2 , x_3, x_4) =
\sum m(2, 8, 9, 12, 15) + D(1, 3, 6, 7).$  Chose the minimum-cost expression
by comparing Product of Sums (POS) and Sum of Products (SOP) forms. [10 marks]
\end{prob}

\begin{prob}
Derive a minimum-cost realization of the four-variable function that is equal to 1 if exactly
two or exactly three of its variables are equal to 1; otherwise it is equal to
0.  [10 marks]
\end{prob}

\begin{prob}
  Find the minimum-cost Sum of Products (SOP) and Product of Sums (POS) forms for the function $f(x_1 , \dots, x_5) =
  \sum m(1, 3, 4, 6, 8, 9, 11, 13, 14, 16, 19, 20, 21, 22, 24, 25) + D(5, 7,
  12, 15, 17, 23).$  Chose the minimum-cost expression by comparing Product of Sums (POS) and Sum of Products (SOP) forms. [10 marks]
\end{prob}

\end{document}
